---
title: "Daily Exercise 05: Penguin Data Analysis"
author: "Mckenna Cooper"
date: "02/12/2025"
format: html
editor: visual
---

\# Attach the \`palmerspenguins\` package

```{r}
library(palmerpenguins)
```

# 1. Examine at the dataset using the ?Help page

```{r}
?penguins
```

# 2. what is the class of the penguins dataset?

```{r}
class(penguins)
```

# 3. what is the structure of the penguins dataset?

```{r}
str(penguins)
```

# 4. what are the dimensions of the penguins dataset?

```{r}
dim(penguins)
```

# 5. what are the column names of the penguins dataset?

```{r}
colnames(penguins)
```

# 6. what type of data is \`flipper_length_mm\` and \`Island\`?

```{r}
class(penguins$flipper_length_mm) # Numeric
class(penguins$island) # Factor (categorical)
```

# 7. what is the mean flipper length of the penguins?

```{r}
mean(penguins$flipper_length_mm, na.rm = TRUE)
```

# 8. what is the standard deviation of flipper length in the penguins?

```{r}
sd(penguins$flipper_length_mm, na.rm = TRUE)
```

# 9. what is the median body mass of the penguins?

```{r}
median(penguins$body_mass_g, na.rm = TRUE)
```

# 10. what is the Island of the 100th penguin?

```{r}
penguins$island[100]
```
